Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-24 paper/sec-doublecounting.tex
small addition

\begin{figure}[ht!]
    \centering
    \begin{overpic}[width=0.6\textwidth, trim=0.cm 11cm 0.cm 10cm, clip=True]{figures/dy-pi.pdf}
        \put (5, 33) {\large $q$}
        \put (20, 37) {\large $q$}
        \put (38, 5) {\large $\ell^+$}
        \put (38, 31) {\large $\ell^-$}
        \put (11, 6) {\large $\gamma$}
        %
        \put (65, 9) {\large $q$}
        \put (73, 30) {\large $q$}
        \put (96, 25) {\large $\ell^-$}
        \put (96, 8) {\large $\ell^+$}
        \put (55, 26) {\large $\gamma$}
    \end{overpic}
    \caption{\label{fig:dy-pi}
    Photon-induced (left) and quark-induced (right) contributions to the Drell-Yan process. In black, the LO process is shown.
    In red, the initial-state splitting leading to the real-emission $q \gamma \to \ell^+ \ell^- q$ is highlighted. Such a 
    real emission enters in the NLO EW corrections.}
\end{figure}
An example is the subtraction of (irreducible) background processes which must not be considered as such. A very blatant case
is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
at $\mathcal O(\alpha^2)$. Because this process is usually thought
as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, often as a background, and it is possibly 
evaluated with different parton densities and/or including (unphysical) higher-order 
corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw} (a similar statement appears also in an older analysis~\cite{Aad:2013iua}), one reads:
\begin{quote}
The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
\end{quote}
Such a distinction, which is unphysical and incorrect in quantum mechanics, may be somehow justified at LO. Beyond this order, it is simply wrong.
Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
includes both kind of topologies discussed above, see Fig.~\ref{fig:dy-pi}. While it is common sense that the QCD counterpart of this subtraction should never 
be performed---nobody would ever
consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses---seemingly it is not so
when EW corrections are considered.

>>>>

\begin{figure}[ht!]
    \centering
    \begin{overpic}[width=0.6\textwidth, trim=0.cm 11cm 0.cm 10cm, clip=True]{figures/dy-pi.pdf}
        \put (5, 33) {\large $q$}
        \put (20, 37) {\large $q$}
        \put (38, 5) {\large $\ell^+$}
        \put (38, 31) {\large $\ell^-$}
        \put (11, 6) {\large $\gamma$}
        %
        \put (65, 9) {\large $q$}
        \put (73, 30) {\large $q$}
        \put (96, 25) {\large $\ell^-$}
        \put (96, 8) {\large $\ell^+$}
        \put (55, 26) {\large $\gamma$}
    \end{overpic}
    \caption{\label{fig:dy-pi}
    Photon-induced (left) and quark-induced (right) contributions to the Drell-Yan process. In black, the LO process is shown.
    In red, the initial-state splitting leading to the real-emission $q \gamma \to \ell^+ \ell^- q$ is highlighted. Such a 
    real emission enters in the NLO EW corrections.}
\end{figure}
An example is the subtraction of (irreducible) background processes which must not be considered as such. A very blatant case
is neutral-current Drell--Yan, where the signal process is an opposite-sign lepton pair, which starts
at $\mathcal O(\alpha^2)$. Because this process is usually thought
as a quark-initiated, $s$-channel mechanism ($q\bar q \to \gamma^*/Z \to \ell^+ \ell^-$), in many analyses the photon-induced component,
$\gamma \gamma \to \ell^+ \ell^-$ in the $t$ channel, is considered as a different process, often as a background, and it is possibly 
evaluated with different parton densities and/or including (unphysical) higher-order 
corrections. For example, in refs.~\cite{Aaboud:2017ffb,Aad:2016zzw} (a similar statement appears also in an older analysis~\cite{Aad:2013iua}), one reads:
\begin{quote}
The photon-induced process, $\gamma\gamma \to \ell \ell$, is simulated at LO using Pythia 8 
and the MRST2004qed PDF set~\cite{Martin:2004dh}. The expected yield for this process also accounts for 
NLO QED/EW corrections from references~\cite{Bardin:2012jk,Bondarenko:2013nu}, which decrease the yield by approximately 30\%.
\end{quote}
Such a distinction, which is unphysical and incorrect in quantum mechanics, may be somehow justified at LO. Beyond this order, it is simply wrong.
Indeed, at $\mathcal O(\alpha^3)$, the reaction $q \gamma \to \ell^+ \ell^- q$ becomes possible, which
includes both kind of topologies discussed above (and needs both in order to yield an IR-finite result), see Fig.~\ref{fig:dy-pi}. While it is common sense that the QCD counterpart of this subtraction should never 
be performed---nobody would ever
consider to \enquote{subtract} the gluon-initiated contribution to top-pair production in top analyses---seemingly it is not so
when EW corrections are considered.
